---
title: "Developing Data Products Course Project Reproducible Pitch"
author: "Soma Chowdhury"
date: "2024-10-01"
output: ioslides_presentation
runtime: shiny
widescreen: true
smaller: true
---

```{r setup, include=FALSE}
library(shiny)
library(plotly)
knitr::opts_chunk$set(echo = FALSE)
```

## Developing Data Products Course Presentation {.smaller}

This presentation serves as a reproducible pitch for a Shiny application developed to meet the requirements of the Developing Data Products peer-graded course assignment. The application showcases the performance of three major stock exchanges over the period from September 2019 to September 2024.

### Application and code links
[ShinyApp](https://schowdhu06.shinyapps.io/ReproduciblePitch/) \
[Github](https://github.com/somachowdhury06/DDP_Module3/tree/gh-pages/Course%20Project/ReproduciblePitch)

## It's all about the data {.smaller}
In the working directory is a csv file Trading Data.csv. It contains big 3 exchange data from Sep 2019 to Sep 2024.
```{r }
  csvdata <- read.csv("Trading data.csv",sep = ",", quote = '"', dec = ".", stringsAsFactors = FALSE)

  csvdata$Date <- as.Date(csvdata$Date, "%m/%d/%Y")

  head(csvdata,5)
```

## User Interaction {.smaller}
The user will be provided with two dropdown menus: one to select a stock exchange and the other to choose a time period. The data for these dropdowns is sourced from the "Trading Data.csv" file. Based on the user's selections, a candlestick chart is generated and displayed.
```{r eval=FALSE, echo=TRUE}
inputPanel(
    selectInput("Exchange", "Exchange:", choices = c("DOW","Nasdaq","S&P"),
                selected = "DOW"),
    selectInput("Period", "Period:", choices = c("Apr-20","Apr-21","Apr-22","May-20","May-21","May-22"),
                selected = "Apr-20")
)
renderPlotly({
    dt <- csvdata[csvdata$Symbol == input$Exchange & csvdata$Period == input$Period, ]
    p <- dt %>% plot_ly(x= ~Date, type="candlestick",
                        open= ~Open, close= ~Close, high= ~High, low= ~Low) %>%
      layout(title=paste(input$Exchange,"Performance", sep = " "))
})
```
## Demo {.smaller}
```{r eval=TRUE}
inputPanel(
  
    selectInput("Exchange", "Exchange:", choices = c("DOW","Nasdaq","S&P"),
                selected = "DOW"),
  

    selectInput("Period", "Period:", choices = c("Apr-20","Apr-21","Apr-22","May-20","May-21","May-22"),
                selected = "Apr-20")
  

)

renderPlotly({
    dt <- csvdata[csvdata$Symbol == input$Exchange & csvdata$Period == input$Period, ]

    p <- dt %>% plot_ly(x= ~Date, type="candlestick",
                        open= ~Open, close= ~Close, high= ~High, low= ~Low) %>%
      layout(title=paste(input$Exchange,"Performance", sep = " "))
})
```

Thank You

